Reconciler: A Template for Reproducible Computational Research Papers

### 2020-08-05 ms.tex
extract reproducibility code from ms.tex to Makefile
[2005.12660]

\documentclass[journal]{IEEEtran}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{booktabs}
\usepackage{datatool}
\usepackage{listings}
\usepackage{makecell}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{trees}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usepackage[hyphens]{url}
\usepackage{hyperref}

@@

\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}

@@

\begin{abstract}
	Previous work in reproducibility focused on providing frameworks to make research reproducible, however fewer work was done on reproducibility certification.
	We propose the Reconciler, that certifies the reproducibility of computational research papers written in \LaTeX.
	Two Docker containers are built and run in separate Virtual Machines (VMs) reproducing the figures, tables and variables (results) of the paper.
	Then the results are used during the \LaTeX\ compilation in each VM, to produce corresponding pdf files.
	Lastly a third VM certifies the research paper as reproducible, if and only if the resulted pdf files are identical.
	The two builds are needed to enable comparison between different builds of the same source code and any non-deterministic stochasticity would produce different pdf files for different builds, thus making the certifier VM report the paper as non-reproducible.
	We release an open source implementation of the Reconciler, that certifies the reproducibility of this paper.
\end{abstract}

@@

A useful \LaTeX\ package for automatically embedding code results variables in \LaTeX\ code is \textit{datatool}.
\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a results code and getting the value of a key named num\_samples.}, captionpos=b]
\DTLloaddb{keys_values}{keys_values.csv}
\DTLfetch{keys_values}{key}{num_samples}{value}
\end{lstlisting}

For example the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the results code:
\begin{itemize}
	\item number of samples of Fig.~\ref{fig:image} is $\DTLfetch{keys_values}{key}{num_samples}{value}$ and
	\item the number of columns of Table~\ref{table:table} is $\DTLfetch{keys_values}{key}{num_columns}{value}$.
\end{itemize}

@@

Using the random seeds and \textit{datatool} we could have deterministic stochasticity that reproduces figures, tables and variables.
For example Fig.~\ref{fig:image} depicts the signal:
\begin{equation}
	f(t) = \DTLfetch{keys_values}{key}{mu}{value} + \DTLfetch{keys_values}{key}{sigma}{value} * Z(t) + t
\end{equation}

,where $Z(t)\sim\mathcal{N}$.

\begin{figure}[h]
	\includegraphics[width=\linewidth]{results/image.pdf}
	\caption{Image example created from results code.}
	\label{fig:image}
\end{figure}

>>>>

\documentclass[journal]{IEEEtran}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{booktabs}
\usepackage{datatool}
\usepackage{listings}
\usepackage{makecell}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{trees}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usepackage[hyphens]{url}

@@

@@

\begin{abstract}
	Previous work in reproducibility focused on providing frameworks to make research reproducible, however fewer work was done on reproducibility certification.
	We propose the Reconciler, which is a template for writing reproducible computational research papers written in \LaTeX.
	A predetermined number of docker containers are built and run in separate Virtual Machines (VMs) reproducing the figures, tables and variables (results) of the paper.
	The previous results are used during the \LaTeX\ compilation in each VM, to produce corresponding pdf files.
	Lastly a third VM certifies the research paper as reproducible, if and only if the resulted pdf files are identical.
	The two builds are needed to enable comparison between different builds of the same source code and any non-deterministic stochasticity would produce different pdf files for different builds, thus making the certifier VM report the paper as non-reproducible.
	We release an open source implementation of the Reconciler, that certifies the reproducibility of this paper.
\end{abstract}

@@

A useful \LaTeX\ package for automatically embedding code results variables in \LaTeX\ code is \textit{datatool}.
\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a results code and getting the value of a key named lr.}, captionpos=b]
\DTLloaddb{keys_values}{keys_values.csv}
\DTLfetch{keys_values}{key}{lr}{value}
\end{lstlisting}

For example the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the results code:
\begin{itemize}
	\item the learning rate is $\DTLfetch{keys_values}{key}{lr}{value}$ and
	\item the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$.
	\item the validation accuracy of the best model is $\DTLfetch{keys_values}{key}{validation_accuracy_best}{value}$.
\end{itemize}

@@

Using the random seeds and \textit{datatool} we could have deterministic stochasticity that reproduces figures, tables and variables.
For example Fig.~\ref{fig:image} depicts the train and validation loss:
\begin{figure}[h]
	\includegraphics[width=\linewidth]{results/image.pdf}
	\caption{Image example created from results code.}
	\label{fig:image}
\end{figure}
